---
title: "XCMS_master"
author: "Katherine Heal"
date: "November 9, 2016"
output: html_document
---
This code is just the XCMS and CAMERA functions.  It should only be run on a high powered computer.

#Load Libraries and source code
```{r Libraries, results='hide', message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr) 
library(ggplot2) 
library(gridExtra) 
library(dplyr) 
library(seqinr) 
library(lubridate)
library(reshape2)
library(tidyr)
library(Hmisc)
library(gtools)
library(cowplot)
require(RColorBrewer)
library(readr)
library(plotly)
library(stringr)
library(xcms) 
library(IPO)

```

#Setup Experiment
This experiment was processed through XCMS on 3/2/17 on personal computer
```{r Set experiment and fraction name.  Raw data file -> "rawdat" -> Fraction (i.e. "CyanoDCM") -> Experiment ("Eddy_samples"), results='hide', message=FALSE, warning=FALSE}

Experiment <- "Gradients2016"
Location <- "/Users/katherine2/Google_Drive/00_XCMS_Working/"
FractionList <- c("HILICNeg", "HILICPos", "CyanoAq", "CyanoDCM")

ExpDIR <-paste(Location, Experiment, sep = "", collapse = NULL)
```

If you have not set up your results directories yet, run this.  Once you have your xcms run, you don't need to rerun this.  As long as the final line is commented out though, its okay.
```{r Set your Directories, grab Params and ISList, results='hide', message=FALSE, warning=FALSE}
FractionDIR <- c()
ResultsDIR <- c()
DataDIR <- c()
for (j in 1:length(FractionList)){
  FractionDIR[j] <- paste(ExpDIR, "/", FractionList[j], sep = "", collapse = NULL)
  ResultsDIR[j] <- paste(FractionDIR[j], "/Results", Sys.Date(), sep = "", collapse = NULL)
 #dir.create(file.path(ResultsDIR[j]), showWarnings = FALSE) #Comment out if you don't need to make the folder i.e. you've already run XCMS and need to redo the next steps
  DataDIR <-  paste(FractionDIR, "/rawdat", sep = "", collapse = NULL)
  }
Dirs <- data.frame(FractionList, FractionDIR, ResultsDIR, DataDIR)

#Modify this to get to your results of choice
 Dirs <- Dirs %>% mutate(ResultsDIR = ResultsDIR %>%
                         str_replace("Results2017-05-11",
                                     "Results2017-05-09")) 
 rownames(Dirs) <- Dirs$FractionList
#write.csv(Dirs, paste(ExpDIR, "/Dirs.csv", sep="", collapse =NULL))#Write this csv when you are satisfied with it - and then comment it out so you don't accidently rewrite your Dirs CSV.
```

Run this if you have already made your directories (to access older results)
```{r, results='hide', message=FALSE, warning=FALSE}
#Get your directories with preferred results
Dirs <- read.csv(paste(ExpDIR, "/Dirs.csv", sep="", collapse =NULL), row.names=1) #If this doesn't work, make sure last line of chunk B4 isn't commented out

#Get your functions
source(paste(Location, "XCMS_funs.R", sep= "", collapse = NULL))
  
#Get your parameters
Params <- read.csv(paste(Location, "Params.csv", sep= "", collapse = NULL), row.names=1)
Params <- Params[ , 1:4]

```

#Do XCMS, get peak Lists, Print out TICs 
Running with PEAKGROUPS on all fractions on 5/10/2017
```{r perform xcms on all fractions, results='hide', message=FALSE, warning=FALSE}
#for (j in 1:length(FractionList)){
j=4
Fraction <- FractionList[j]
DataDIR <- as.character(Dirs[Fraction, "DataDIR"])
DatFiles <- list.files(DataDIR, recursive = TRUE, full.names = TRUE)
DatFiles <- DatFiles[grepl(".mzXML", DatFiles)]

#Save your parameters used for your xcms-ing
write.csv(Params[,1:4], paste(Dirs[Fraction, "ResultsDIR"], sep = "","/Params_used.csv", collapse = NULL), row.names = TRUE)

#Do the XCMS
setwd(DataDIR)
xset1 <- doPeakPick(DatFiles)
xset1 <- dogrouping(c(xset1))

setwd(as.character(Dirs[Fraction, "ResultsDIR"]))
save(xset1,  file="xset1_initial.RData")

#Do RT Correction (of some iterations)
for (k in 1:Params["RTITs", Fraction]){
xset1 <- doRetcorPG(xset1) #Change to doRetcor for obiwarp, doRetcorPG for peak groups (better for cyano)
xset1 <- dogrouping(xset1)
}
save(xset1,  file="xset2_RTCorrected.RData")

#RT Correction plot
png("RTCorrplot.png", width = 4, height = 5, units = "in", res = 300) 
plotrt(xset1, leg = F, densplit = T)
dev.off() 

#Write unfilled dataframe
Peaks.unfilled <- peakTable(xset1) 
Peaks.unfilled$MassFeature <- paste("I", round((Peaks.unfilled$mz),digits=4), "R", round( Peaks.unfilled$rt/60, digits=2), sep="")
Peaks.unfilled$groupname <- groupnames(xset1)
Peaks.unfilled$RT <- Peaks.unfilled$rt/60
Peaks.unfilled$Fraction <- Fraction
write.csv(Peaks.unfilled, "xset.unfilled.csv")

#Fill in peaks, write dataframe
xset3 <-  fillPeaks(xset1)
save(xset3,  file = "xset3_RTCorrected_PeaksFilled.RData")

Peaks.filled <- peakTable(xset3)
Peaks.filled$MassFeature <- paste("I", round((Peaks.filled$mz),digits=4), "R", round( Peaks.filled$rt/60, digits=2), sep="")
Peaks.filled$groupname <- groupnames(xset3)
Peaks.filled$RT <- Peaks.filled$rt/60
Peaks.filled$Fraction <- Fraction

write.csv(Peaks.filled, "xset.allpeaks.csv")
getTICs(xcmsSet=xset3, pdfname="TICs.pdf",rt="corrected")

PPS <- as.data.frame(calcPPS(xset3))
write.csv(PPS, "PPS_results.csv")

#}
```

#Run Camera_Function and run the camera post processing ---- 
Needs Camera_Fuction.R , CAMERApostprocessing.fuction.R, XCMS results
This was run on on peak group retention time correlated data on 5/10/17
```{r Calculate adducts and isotopes for mass features and calculate neutral mass for ions with two or more adducts, results='hide', message=FALSE, warning=FALSE'}
source(paste(Location, "Camera_Function.R", sep=""))
source(paste(Location, "CAMERApostprocessing.function.R", sep=""))
#for (j in 1:length(FractionList)){
  j=4
  Fraction <- FractionList[j]
  load(paste(as.character(Dirs[Fraction, "ResultsDIR"]), "/xset3_RTCorrected_PeaksFilled.RData", sep=""))
  
  if (Fraction == "HILICNeg") {Pol = "negative"} else {Pol = "positive"} 
  CAMERAlist <- camera (xset3, Polarity = Pol, PPM = 5) 
  save(CAMERAlist, file = paste(as.character(Dirs[Fraction, "ResultsDIR"]), "/CAMERAlist.RData", sep=""))
  
  xset.annot <- CAMERAlist[[1]] 
  xsaFA <- CAMERAlist[[2]] 
  IonList <- camerapostprocess(xsaFA, xset.annot) 
  save(IonList, file = paste(as.character(Dirs[Fraction, "ResultsDIR"]), "/IonList.RData", sep=""))
  OtherIons <- IonList[[3]] 

#}
```


#Do Very basic Filtering on Data
Needs XCMS only
ReRun on 5/31/17, make filter more stark
```{r Making Averages and basic filtering}
for (j in 1:4){
 
Fraction <- FractionList[j]
  setwd(as.character(Dirs[Fraction, "ResultsDIR"]))
  Peaks.filled <- read.csv("xset.allpeaks.csv")
  
  #Get data file names
  DatNames <- colnames(Peaks.filled)[grepl("X17", colnames(Peaks.filled))]
  
  #Specifiy which runs are Blks, samples, and treatments
  Blks <- DatNames[grepl("_Blk_", DatNames)]
  Samps <- DatNames[grepl("_Smp_", DatNames)]
  Poos <- DatNames[grepl("_Poo_", DatNames)]

  
  
   #Set rt max and min
  rtminparam <- Params["RTMIN", Fraction]
  rtmaxparam <- Params["RTMAX", Fraction]
  
 if (length(Blks) > 1) {Peaks.filled$AveBlank<- rowMeans(Peaks.filled[, Blks])} else {Peaks.filled$AveBlank<- Blks[1]}
  Peaks.filled$AveSmp<- rowMeans(Peaks.filled[, Samps])
  Peaks.filled$AvePoo <- rowMeans(Peaks.filled[, Poos])
  Peaks.filtered <- Peaks.filled %>%
    filter(rt > rtminparam) %>%
    filter(rt < rtmaxparam) %>%
     filter(AvePoo > 10*AveBlank)  %>%
    filter(npeaks > (0.25*length(Samps))) %>%
    filter(AvePoo > 5000)
    
  setwd(as.character(Dirs[Fraction, "ResultsDIR"]))
  write.csv(Peaks.filtered, "xset.filtered.csv")
}
```

#Now do BMIS on each fraction separately

