---
title: "XCMS_master"
author: "Katherine Heal"
date: "November 9, 2016"
output: html_document
---
This code is just the XCMS and CAMERA functions.  It should only be run on a high powered computer.


#Load Libraries and source code
```{r Libraries, results='hide', message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr) 
library(ggplot2) 
library(gridExtra) 
library(dplyr) 
library(seqinr) 
library(lubridate)
library(reshape2)
library(tidyr)
library(Hmisc)
library(gtools)
library(cowplot)
require(RColorBrewer)
library(readr)
library(plotly)
library(stringr)
library(xcms) 
library(IPO)

```

#Setup Experiment
```{r Set experiment and fraction name.  Raw data file -> "rawdat" -> Fraction (i.e. "CyanoDCM") -> Experiment ("Eddy_samples"), results='hide', message=FALSE, warning=FALSE}

Experiment <- "1335_B12Light_Exp"
Location <- "/Users/katherine2/Google Drive/XCMS_Working/"
FractionList <- c("HILICNeg", "HILICPos", "CyanoAq", "CyanoDCM")

#Pick 2 IDs that will work to call Biological replicates to compared for the QC step
Treat1ID <- "_LB12"
Treat2ID <- "_RB12"

ExpDIR <-paste(Location, Experiment, sep = "", collapse = NULL)

gmail <- "riseheathenorleak@gmail.com" #If you want emails sent when things move along.  MUST BE GMAIL
```

If you have not set up your results directories yet, run this.  Once you have your xcms run, you don't need to rerun this.  As long as the final line is commented out though, its okay.
```{r Set your Directories, grab Params and ISList, results='hide', message=FALSE, warning=FALSE}
FractionDIR <- c()
ResultsDIR <- c()
DataDIR <- c()
for (j in 1:length(FractionList)){
  FractionDIR[j] <- paste(ExpDIR, "/", FractionList[j], sep = "", collapse = NULL)
  ResultsDIR[j] <- paste(FractionDIR[j], "/Results", Sys.Date(), sep = "", collapse = NULL)
 #dir.create(file.path(ResultsDIR[j]), showWarnings = FALSE) #Comment out if you don't need to make the folder i.e. you've already run XCMS and need to redo the next steps
  DataDIR <-  paste(FractionDIR, "/rawdat", sep = "", collapse = NULL)
  }
Dirs <- data.frame(FractionList, FractionDIR, ResultsDIR, DataDIR)

#Modify this to get to your results of choice
 Dirs <- Dirs %>% mutate(ResultsDIR = ResultsDIR %>%
                         str_replace("Results2017-02-14",
                                     "Results2017-02-13")) 
 rownames(Dirs) <- Dirs$FractionList
#write.csv(Dirs, paste(ExpDIR, "/Dirs.csv", sep="", collapse =NULL))#Write this csv when you are satisfied with it - and then comment it out so you don't accidently rewrite your Dirs CSV.
```

Run this if you have already made your directories (to access older results)
```{r, results='hide', message=FALSE, warning=FALSE}
#Get your directories with preferred results
Dirs <- read.csv(paste(ExpDIR, "/Dirs.csv", sep="", collapse =NULL), row.names=1) #If this doesn't work, make sure last line of chunk B4 isn't commented out

#Get your functions
source(paste(Location, "XCMS_funs.R", sep= "", collapse = NULL))
  
#Get your parameters
Params <- read.csv(paste(Location, "Params.csv", sep= "", collapse = NULL), row.names=1)
Params <- Params[ , 1:4]

#Get your ISMasterList
ISMasterList <- read.csv(paste(Location, "ISlist.csv", sep= "", collapse = NULL))
ISMasterList$lowmz <- ISMasterList$m.z - (ISMasterList$m.z*5)/1e6
ISMasterList$highmz <- ISMasterList$m.z + (ISMasterList$m.z*5)/1e6

```

#Do XCMS, get peak Lists, Print out TICs 
Was re-run on 2/13/17 for all fractions to include pooled samples
```{r perform xcms on all fractions, results='hide', message=FALSE, warning=FALSE}
for (j in 1:length(FractionList)){
Fraction <- FractionList[j]
DataDIR <- as.character(Dirs[Fraction, "DataDIR"])
DatFiles <- list.files(DataDIR, recursive = TRUE, full.names = TRUE)
DatFiles <- DatFiles[grepl(".mzXML", DatFiles)]

#Save your parameters used for your xcms-ing
#setwd(as.character(Dirs[Fraction, "ResultsDIR"]))
write.csv(Params[,1:4], paste(Dirs[Fraction, "ResultsDIR"], sep = "","/Params_used.csv", collapse = NULL), row.names = TRUE)

#Do the XCMS
setwd(DataDIR)
xset1 <- doPeakPick(DatFiles)
xset1 <- dogrouping(c(xset1))

setwd(as.character(Dirs[Fraction, "ResultsDIR"]))
save(xset1,  file="xset1_initial.RData")

#Do RT Correction (of some iterations)
#for (k in 1:Params["RTITs", Fraction]){
xset1 <- doRetcorPG(xset1) 
xset1 <- dogrouping(xset1)
#}

#RT Correction plot
png("RTCorrplot.png", width = 4, height = 5, units = "in", res = 300) 
plotrt(xset1, leg = F, densplit = T)
dev.off() 
save(xset1,  file="xset2_RTCorrected.RData")

#Write unfilled dataframe
Peaks.unfilled <- peakTable(xset1) 
Peaks.unfilled$MassFeature <- paste("I", round((Peaks.unfilled$mz),digits=4), "R", round( Peaks.unfilled$rt/60, digits=2), sep="")
Peaks.unfilled$groupname <- groupnames(xset1)
Peaks.unfilled$RT <- Peaks.unfilled$rt/60
Peaks.unfilled$Fraction <- Fraction
write.csv(Peaks.unfilled, "xset.unfilled.csv")

#Fill in peaks, write dataframe}
xset3 <-  fillPeaks(xset1)
save(xset3,  file = "xset3_RTCorrected_PeaksFilled.RData")
Peaks.filled <- peakTable(xset3)
Peaks.filled$MassFeature <- paste("I", round((Peaks.filled$mz),digits=4), "R", round( Peaks.filled$rt/60, digits=2), sep="")
Peaks.filled$groupname <- groupnames(xset3)
Peaks.filled$RT <- Peaks.filled$rt/60
Peaks.filled$Fraction <- Fraction

write.csv(Peaks.filled, "xset.allpeaks.csv")
getTICs(xcmsSet=xset3, pdfname="TICs.pdf",rt="corrected")

PPS <- as.data.frame(calcPPS(xset3))
write.csv(PPS, "PPS_results.csv")

##Alert that we're done
library(sendmailR)
from <- gmail
to <- gmail
subject <- "XCMS done"
body <- list(paste(Fraction, "XCMS done!", sep = " "))
sendmail(from, to, subject, body,
         control=list(smtpServer="ASPMX.L.GOOGLE.COM"))
}


```

#Run Camera_Function and run the camera post processing ---- 
Needs Camera_Fuction.R , CAMERApostprocessing.fuction.R, XCMS results
Was re-run on 2/13/17 for all fractions to include pooled samples
```{r Calculate adducts and isotopes for mass features and calculate neutral mass for ions with two or more adducts, results='hide', message=FALSE, warning=FALSE'}
source(paste(Location, "Camera_Function.R", sep=""))
source(paste(Location, "CAMERApostprocessing.function.R", sep=""))
for (j in 1:length(FractionList)){
  Fraction <- FractionList[j]
  load(paste(as.character(Dirs[Fraction, "ResultsDIR"]), "/xset3_RTCorrected_PeaksFilled.RData", sep=""))
  
  if (Fraction == "HILICNeg") {Pol = "negative"} else {Pol = "positive"} 
  CAMERAlist <- camera (xset3, Polarity = Pol, PPM = 5) #started at 10:24 for HILCNeg
  save(CAMERAlist, file = paste(as.character(Dirs[Fraction, "ResultsDIR"]), "/CAMERAlist.RData", sep=""))
  
  xset.annot <- CAMERAlist[[1]] 
  xsaFA <- CAMERAlist[[2]] 
  IonList <- camerapostprocess(xsaFA, xset.annot) 
  save(IonList, file = paste(as.character(Dirs[Fraction, "ResultsDIR"]), "/IonList.RData", sep=""))
  OtherIons <- IonList[[3]] 

  ##Alert that we're done
  library(sendmailR)
  from <- gmail
  to <- gmail
  subject <- "CAMERA done"
  body <- list(paste(Fraction, "CAMERA done!", sep = " "))
  sendmail(from, to, subject, body,
           control=list(smtpServer="ASPMX.L.GOOGLE.COM"))
}
```

